\documentclass[12pt]{moderncv}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FORMAT & THEME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[margin=1in]{geometry}

% Theme options
%     casual (default)
%     classic
%     oldstyle
%     banking
%     fancy
% Color schemes
%     black
%     blue
%     burgundy
%     green
%     grey
%     orange
%     purple
%     red

\moderncvtheme{banking}
\moderncvcolor{purple}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PUBLICATIONS (see also below)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[sorting=ydnt,doi=false,isbn=false,url=false,eprint=false]{biblatex}
\addbibresource{publications.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CONTACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\firstname{Samuel E.}
\familyname{Reynolds}

\phone{971-703-8819}
\email{ser6@pdx.edu}
\homepage{sites.google.com/view/samreynolds}

\social[researchgate]{Samuel-Reynolds-4}
\social[github]{samreynoldsmath}
\social[orcid]{0000-0002-7489-6474}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MAIN BODY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
    \cventry{2024 (Expected)}{Ph.D. in Mathematical Sciences}{Portland State University}{Portland, Oregon, USA}{}{}
    \cventry{2020}{M.S. in Mathematics}{Portland State University}{Portland, Oregon, USA}{}{}
    \cventry{2017}{B.S. in Mathematics}{Portland State University}{Portland, Oregon, USA}{Magna cum laude, Departmental honors}{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% RESEARCH INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research Interests}
    My primary research focus is numerical methods for partial differential equations.
    Specifically, I am working on a finite element method using nonstandard meshes incorporating cells with curved edges and holes, using ideas from virtual element methods and boundary element methods.
    I also have experience in numerical optimization and high performance computing.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Positions}

    \subsection{Research positions}

        \cventry{2016--2024}{Research assistant}{Fariborz Maseeh Dept. of Math. \& Stats., PSU}{Portland, OR}{}{Advisor: Jeffrey Ovall}

        \cventry{2022}{Computing scholar}{Lawrence Livermore National Laboratory}{Livermore, California}{summer internship}{Mentor: Julian Andej}

        \cventry{2021}{Givens associate}{Argonne National Laboratory}{Chicago, Illinois}{summer internship}{Mentor: Richard Tran Mills}

    \subsection{Education positions}

        \cventry{2019--2020}{Graduate teaching assistant}{Fariborz Maseeh Dept. of Math. \& Stats., PSU}{Portland, OR}{}{Supervisor: Andy Flight}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COMPUTING SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Computing Skills}

    Python, MATLAB, C, C++, Wolfram Mathematica, MS Excel, \LaTeX, git, Linux, MacOS, MS Windows

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AWARDS AND HONORS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\break
\section{Awards and Honors}

    \cvline{NSF Research Training Group Graduate Fellowship (2022--2023)}{National Science Foundation}

    \cvline{Excellence in Remote Teaching Award (2020)}{Fariborz Maseeh Dept. of Math. \& Stats., PSU}

    \cvline{Level III (Master) Tutor Certification (2019)}{College Reading \& Learning Association}

    \cvline{F. S. Cater Prize (2019)}{Fariborz Maseeh Dept. of Math. \& Stats., PSU}

    \cvline{Christine and David Vernier STEM Scholarship (2016)}{PSU College of Liberal Arts and Sciences}

    \cvline{Oregon NASA Space Scholarship (2015)}{Oregon Space Grant Consortium}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PUBLICATIONS (see also above)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% using the biblatex package
\renewbibmacro{in:}{}
\nocite{*}
\printbibliography[title={Publications}]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADDITIONAL INFORMATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Further Information}

    \cvline{Also known as}{Sam Reynolds}
    \cvline{Pronouns}{he/him/his}
    \cvline{Country of citizenship}{United States of America}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}